% LaTeX file for resume A
% This file uses the resume document class (res.cls)

\documentclass[margin]{res} 
% the margin option causes section titles to appear to the left of body text 
\textwidth=5.0in % increase textwidth to get smaller right margin
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\usepackage[none]{hyphenat}

\begin{document}

\name{Josh J. Meyer\\[12pt]}

\address{{\bf Contact Information}\\jjmeyer0@gmail.com}
\address{{\bf } \\}

\begin{resume} 

\section{Computer Skills}
\begin{tabular}{l p{4in}}
  \underline{Languages:} & Java, Bash\\
  \underline{Software:} & Git, IntelliJ IDEA \\
  \underline{Other:} & Linux, Mac OS X, Spring, Guice, Maven, JUnit, JSON, XML, NiFi, Oozie, Hadoop, Docker, Kubernetes
\end{tabular}

\section{Online}
\begin{itemize} \itemsep -2pt
\item github.com/jjmeyer0
\item linkedin.com/in/jjmeyer0
\end{itemize}

\section{Experience}
 {\bf Lead Software Engineer, March 2019 to Present\\
 Target, Minneapolis, Minnesota}
 \begin{itemize} \itemsep -2pt
 \item Supported, maintained, and implemented features on internal ELT application and scheduling platform.
 \item Worked on a custom ELT application and scheduling platform that ran ~80k jobs a day.
 \item Helped set direction of the custom ELT application and scheduling platform by creating and planning releases.
 \item Mentored and taught new team members the platform I worked on.
 \item Collaborated with other platform teams to ensure Target's internal platforms integrated with our platform to give our end users the best possible experience.
 \end{itemize}
 
 {\bf Senior Software Engineer, September 2017 to March 2018\\
 Target, Minneapolis, Minnesota}
 \begin{itemize} \itemsep -2pt
 \item Instilled a proper software development lifecycle within the team.
 \item Broke monolithic application into smaller independently deployable applications.
 \item Enabled the platform to schedule jobs across platforms (Kubernetes and local server).
 \item Helped scale the scheduler to run ~2.1 million jobs a month.
 \item Supported and enabled AutomationPortal, a custom built ELT and self service scheduling tool that served Target's Analysts, Data Engineers, and Data Scientists.
 \end{itemize}

 {\bf  Senior Consultant, February 2016 to September 2017\\
 Hortonworks, Minneapolis, Minnesota}
 \begin{itemize} \itemsep -2pt
 \item Worked as a professional services consultant.
 \item Worked for a large financial services company as a Hadoop Developer. 
 \item Helped create and maintain a data orchestration tool that allowed a business user to ingest their data.
 \item The orchestration tool moved data from a local landing zone to HDFS and executed Hive scripts and applied Ranger policies to newly create tables, directories, and databases.
 \item Instilled a focus of unit testing. Helped increase unit test coverage by two times.
 \item Contributed to Apache NiFi.
 \item Contributed to Apache Metron.
 \item Created example code bases for common use cases. Specifically for Ranger, Hadoop, Pig, and Spark.
 \end{itemize}
 
{\bf  Software Engineer, September 2014 to January 2016\\
 The Nerdery, Minneapolis, Minnesota}
 \begin{itemize} \itemsep -2pt
 \item Automated over 200 processes that used over 1000 data feeds using Apache Falcon and Oozie.
 \item Helped instill a maintainable and simple software development lifecycle within our group of developers.
 \item Assisted in automating processes that handled terabytes of data each day. The whole dataset was \textgreater 2 petabytes.
 \item Developed and maintained a tool that would ingest data into HDFS on a user defined schedule. 
 \item Created tools to help automate generation of 1200+ Falcon entities.
 \item Lead a team of three developers. This included prioritizing and delegating tasks to each of the developers.
 \end{itemize}

 {\bf  Application Developer II, March 2013 to September 2014\\
 Federal Home Loan Bank of Des Moines, Des Moines, Iowa}
 \begin{itemize} \itemsep -2pt
 \item Played a key role in designing, implementing, testing, and maintaining a 20+ million dollar project that took 2.5 years to complete.
 \item Created, designed, and maintained a common data format to allow different systems to communicate.
 \item Wrote integration software that allows systems to communicate in real time using ActiveMQ and Camel.
 \item Contributed to workflow and process changes for our deliveries to production (e.g., helped introduce some agile practices).
 \item Responsible for the maintenance and development of Federal Home Loan Bank of Des Moines' infrastructure and applications.
 \end{itemize}

 {\bf  Application Developer I, January 2012 to March 2013\\
   Federal Home Loan Bank of Des Moines, Des Moines, Iowa}
 \begin{itemize} \itemsep -2pt
 \item Refactored Federal Home Loan Bank of Des Moines' member facing web application. This enabled the development team to easily redesign and add new features.
 \item Helped create new processes for the development team (e.g., coding standards, code reviews, occasional pair programming). 
 \item Worked on Core Banking System project. A project that will greatly improve the trade capture processes by replacing a 10+ year old systems.
 \item Created proof of concept applications for the Core Banking System project.
 \item Installed and maintained a Wiki site that allowed people to collaborate and share knowledge more easily.
 \end{itemize}
  
{\bf  Research Experience, May 2010 to December 2011\\
 University of Iowa, Iowa City, Iowa}
 \begin{itemize} \itemsep -2pt
 \item Created and updated tools that allow the process of developing programming languages run more efficiently.
 \item Aided in the design and implementation of a meta-language that allows the user to create common functions.
 \item Attended weekly lectures that were lead by current University of Iowa graduate students.
 \item Assisted in creating a compiler for Blaise, a new research programming language, created by Professor Aaron Stump. Blaise is a functional programming language that requires explicit allocation/deallocation of memory.
 \item Maintained tools I aided in creating.
 \end{itemize}

 \section{Education} 
{\bf B.S. in Computer Science, May 2011\\
Minor in Art, May 2011}\\
University of Iowa, Iowa City, IA

 \section{Certifications}
\begin{itemize} \itemsep -2pt
\item Oracle Certified Associate, Java SE 7 Programmer
\item HDP Certified Administrator
\item HDP Certified Developer
\item Professional Scrum Developer I
\end{itemize}

\section{Open Source Contributions}
\begin{itemize} \itemsep -2pt
\item Apache Metron
\item Apache NiFi
\end{itemize}

\end{resume} 
\end{document} 
